Proposed Solution

### 2017-01-22 CAV17/secs/learner.tex
more learner and commands

The goal of the learner is to derive rules from the intermediate representation of the training set generated by the translator.
We an interface for uses to define rules that should be learned.
Each instance of the interface corresponds to a different class of of configuration errors, such as missing entry errors, ordering errors, and fine-grained value correlation errors. 
These errors can cause total system failures, but can also be more insidious, for example slowing down the system only when the server load increases beyond a certain threshold.

>>>>

The goal of the learner is to derive rules from the intermediate representation of the training set generated by the translator.
We describe an interface to define the different classes of rules that should be learned.
Each instance of the interface corresponds to a different class of of configuration errors, such as missing entry errors, ordering errors, and integer correlation errors. 
These errors can cause total system failures, but can also be more insidious, for example slowing down the system only when the server load increases beyond a certain threshold.

%TODO define rule

We use an approach similar to \textit{association rule learning}~\cite{agrawal1993mining}, a technique that can be summarized as inductive machine learning.
Association rule learning is best suited to learn rules over sets of keys, which in the configuration domain are integer correlation and missing keyword rules.
Sequence mining~\cite{} is a more appropriate technique for learning ordering rules, and again another approach may be a better fit for rules over a single keyword, as is needed for probabilistic types.
We highlight here only two key metrics from these approaches that are most relevant to verification tasks; \textit{support} and \textit{confidence}.

Support is the number of times the set of keywords in the proposed rule will be 
Confidence is

### 2017-01-22 CAV17/secs/postanal.tex
more learner and commands

\iffalse

Define a graph with labeled, weighted edges $G = (V,E)$ such that:

    V \def { keywords }

@@

    E \def { (v_1, v_2, l, w) }

@@

Structure:
    - Definition
        > Degree (in-degree + out-degree) for each node

@@

            IN_DEGREE(k) = ||

            \forall keyword k \in rules, in_degree()

@@

    - Semantics
        > Intuitively, keywords that are seen together more often
          with defined relationships
          are more likely to generate rules within the learner.
          (it would be nice to show this with a quick derivation)

@@

            - adequate support
                we have seen the keywords together x number of times

            - adequate confidence
                how many times out of the x number of times 
                was the relationship true?

    - Open Questions
        > What is the difference between {\it important} rules and
          {\it rules we are more sure about}?

@@

\subsection{Complexity Measure}

INCLUDE SHORT BACKGROUND ON CODE COMPLEXITY. We define a measurement
of complexity based on the calculated correlation. The presented
metric is a heuristic that intends to approximate the quetion, 
{\it how much redundancy exists in a configuration file, when considering
probabilistic constraints imposed by the problem domain}?

@@

\fi

>>>>

Define a graph with labeled, weighted edges $G = (V,E)$ such that:
\iffalse
    V \def { keywords }

@@

    E \def { (v_1, v_2, l, w) }
\fi

@@

\para {Definition}
Degree (in-degree + out-degree) for each node

@@

\iffalse    IN_DEGREE(k) = ||

    $\forall keyword k \in rules, in\_degree()$
\fi

@@

\para {Semantics}
Intuitively, keywords that are seen together more often with defined relationships are more likely to generate rules within the learner.
 (it would be nice to show this with a quick derivation)

@@

1) adequate support -we have seen the keywords together x number of times

2) adequate confidence - how many times out of the x number of times was the relationship true?

\iffalse
- Open Questions
> What is the difference between {\it important} rules and
  {\it rules we are more sure about}?

@@

\fi
\subsection{Complexity Measure}

INCLUDE SHORT BACKGROUND ON CODE COMPLEXITY. We define a measurement
of complexity based on the calculated correlation. The presented
metric is a heuristic that intends to approximate the quetion, 
 how much redundancy exists in a configuration file, when considering
probabilistic constraints imposed by the problem domain?

@@

### 2017-01-22 CAV17/secs/trans.tex
more learner and commands

Formally, a probabilistic types is a set of counts over a set $\mathcal{T}$ of basic types.
A probabilistic type, $\tilde{\tau} \in \tilde{\mathcal{T}}$, is a set of pairs $\{(\tau_1, c_1),\ldots,(\tau_n, c_n)\}$, such that $\tau_i \in \mathcal{T}$, $c_i \in \mathbb{Z}$. 
A keyword has a probabilistic type, expressed $k:\tilde{\tau}$, which without any evidence remains as {\scriptsize EMPTY}.
The count for $(\tau_i,c_i) \in \tilde{\tau}$ is incremented each time a new example value that matches to type $\tau_i$ is encountered for a particular key, as shown in the {\scriptsize BOOL\_INT} and {\scriptsize BOOL} rules.

\begin{mathpar}
\hspace{-0.4cm} %no idea why, but this is better than \centering here
\inferrule* [Right=Empty]
{\\}
{k:[\ast = 0]}
\and
\inferrule* [Right=bool\_int]
{(k,v) \in C \\ v \in \{0,1\}}
{k:[int\pluseq 1,bool\pluseq 1]}
\\
\and
\inferrule* [Right=bool\_resolve]
{k:\tilde{\tau} \\ \tilde{\tau} \models bool \geq 2 \land \ast \leq 1}
{k :: bool}
\\
\and
\inferrule* [Right=bool]
{(k,v) \in C \\ v \in \{ON,OFF\}}
{k:[bool\pluseq 1]}
\and
\inferrule* [Right=eq\_rule]
{k1 :: \tau \\ k2 :: \tau \\ \tau \in \mathcal{T}}
{eq(k1,k2) :: Rule}
\end{mathpar}

In the {\scriptsize BOOL\_RESOLVE} rule, a keyword with a probabilistic type $k : \tilde{\tau} \in \tilde{\mathcal{T}}$ can be resolved to a basic type with enough evidence.
The definition of enough evidence must be empirically determined by the user depending on the quality of the learning set.
In this case, we allow a probabilistic type to resolve to a boolean if we have two counts for boolean, and no more than one count for any other basic type ($\ast$).
We use the notation, $\tilde{\tau} \models p$, to denote a probabilistic type whose counts hold on the predicate $p$.
Taking the type inference rules above, we can run an example inference on the sample training set in Figure~\ref{fig:tset}.
We would derive the probabilistic type \texttt{bar}$:[bool=3,int=1]$, which then resolves to \texttt{bar}$::bool$.

@@

\begin{mathpar}
\hspace{-0.8cm} %no idea why, but this is better than \centering here
\inferrule* [Right=int\_resolve]
{k:\tilde{\tau} \\ \tilde{\tau} \models int \geq 1}
{k :: int}
\and
\inferrule* [Right=order\_rule]
{k1,k2 \in C \\ k1 \neq k2}
{ord(k1,k2) :: Rule}
\end{mathpar}

>>>>

A probabilistic type is a set of counts over a set $\mathcal{T}$ of basic types.
Formally, we define a space of probabilistic types $\tilde{\mathcal{T}}$, where $\ptype=\{(\tau_1, c_1),\ldots,(\tau_n, c_n)\}$ is a set of pairs, such that $\ptype \in \tilde{\mathcal{T}}, \tau_i \in \mathcal{T}$, $c_i \in \mathbb{Z}$. 
Every keyword has a probabilistic type, expressed $k:\ptype$, which, without any evidence, remains {\scriptsize EMPTY}.
The count for $(\tau_i,c_i) \in \ptype$ is incremented each time a new example value that matches to type $\tau_i$ is encountered for a particular key, using the update notation $\update$.

\begin{mathpar}
\hspace{-0.4cm} %no idea why, but this is better than \centering here
\inferrule* [Right=Empty]
{\\}
{k:[\ast = 0]}
\and
\inferrule* [Right=bool\_int]
{(k,v) \in C \\ v \in \{0,1\} \\ k:\ptype}
{k:\ptype\update[int\pluseq 1,bool\pluseq 1]}
\and
\inferrule* [Right=bool]
{(k,v) \in C \\ v \in \{ON,OFF\} \\ k:\ptype}
{k:\ptype\update[bool\pluseq 1]}
\\
\and
\inferrule* [Right=bool\_resolve]
{k:\ptype \\ \ptype \models bool \geq 2 \land \ast \leq 1}
{k :: bool}
\\
\and
\inferrule* [Right=eq\_rule]
{k1 :: \tau \\ k2 :: \tau \\ \tau \in \mathcal{T}}
{eq(k1,k2) :: Rule}
\end{mathpar}

In the {\scriptsize BOOL\_RESOLVE} rule, a keyword with a probabilistic type $k : \ptype \in \tilde{\mathcal{T}}$ can be resolved to a basic type with enough evidence.
The definition of enough evidence must be empirically determined by the user depending on the quality of the learning set.
In this case, we allow a probabilistic type to resolve to a boolean if we have two counts for boolean, and no more than one count for any other basic type ($\ast$).
We use the notation, $\ptype \models p$, to denote a probabilistic type whose counts hold on the predicate $p$.
Taking the type inference rules above, we can run an example inference on the sample training set in Figure~\ref{fig:tset}.
We would derive the probabilistic type \texttt{bar}$:[bool=3,int=1]$, which then resolves to \texttt{bar}$::bool$.

@@

\begin{mathpar}
\hspace{-0.8cm} %no idea why, but this is better than \centering here
\inferrule* [Right=int\_resolve]
{k:\ptype \\ \ptype \models int \geq 1}
{k :: int}
\and
\inferrule* [Right=order\_rule]
{k1,k2 \in C \\ k1 \neq k2}
{ord(k1,k2) :: Rule}
\end{mathpar}
